\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-05-15 paper/ms.tex
Marsden
Command line options

% Need this after the abstract
\setlength{\parindent}{0pt}
\setlength{\parskip}{8pt}

@@

@@

\section*{Acknowledgements}
It is a pleasure to thank Anna Pancoast (Harvard),
Ewan Cameron (Oxford), David Hogg (NYU), and Daniela Huppenkothen (NYU)
for valuable discussions.

>>>>

%% Need this after the abstract
%\setlength{\parindent}{0pt}
%\setlength{\parskip}{8pt}

@@

\section{Running models}

\subsection{Options}
A plain-text file called OPTIONS resides in the directory from which you
execute a run.

Additional options are available on the command line. These are:\\

\code{-o <filename>}\\
This option loads the \pkg{DNest4} options from the specified file, allowing
an alternative to the default OPTIONS.\\

\code{-s <seed>}\\
This seeds the random number generator with the specified value. If unspecified, the system time is used.\\

\code{-d <filename>}\\
Load data from the specified file, if required.\\

\code{-c <value>}\\
Standard DNS creates levels with a volume ratio of approximately
$e\approx 2.71828$. To use a different value, such as 10, use this option.\\

\code{-t <num\_threads>}\\
Run on the specified number of threads. The default is 1.

@@

\section*{Acknowledgements}
It is a pleasure to thank Anna Pancoast (Harvard),
Ewan Cameron (Oxford), David Hogg (NYU), and Daniela Huppenkothen (NYU)
for valuable discussions. BJB was supported by a Marsden Fast-Start grant
from the Royal Society of New Zealand.
